Constructing the transition graphs of interacting hysterons

### 2022-05-30 Paper_draft.tex
Changed structure for section about constructing graphs
Added figure sketch for exchange symmetry & garden-of-Eden states
Removed figure sketch for base graph counting
Added piece about exchange symmetry

%We here explain our method for finding the possible graphs via candidate graphs. We first show how the design inequalities are obtained for a single graph. We explain how one can check if the set of inequalities has a solution using the well-established method of Fourier-Motzkin elimination. Secondly, we detail how one can construct a list of candidate graphs from all combinations of possible transition graphs. Finally, we improve on the candidate graphs method by establishing a notion of base graphs.

@@

@@

@@

@@

\subsection{Base graphs}

@@

    \includegraphics[width=0.5\textwidth]{basegraphs_counting_sketch.png}
    \caption{(a) Construction of possible base graphs from all combinations of $l=1$ transition graphs. (b) A pair of example graphs which are equal when garden-of-Eden states are ignored.}

@@

\subsection{Avalanches}

>>>>

@@

\subsection{Candidate graphs}

@@

    \includegraphics[width=0.5\textwidth]{exchange_plus_goe.png}
    \caption{Considerations for removing duplicate graphs: a) exchange symmetry and b) garden-of-Eden states.}
    \label{fig:exchangeplusgoe}
\subsubsection{Exchange symmetry}
The hysterons in our model are considered as indistinguishable particles. That is, when we define the state $S = \{s_1, s_2, ..., s_N\}$, the labelling of hysterons 1 through N is arbitrary. As a result, when two graphs only differ from one another by the ordering of the hysterons 1, 2, ..., N, we consider the graphs to be the same (Fig. \ref{fig:exchangeplusgoe}a).\\
To account for exchange symmetry, we fix the order in which hysterons 1, 2, ..., N flip up when increasing the external field from the ground state. For example, for $N=3$, we have that hysteron 3 flips up first from the state 000, hysteron 2 flips up first from 001, and trivially hysteron 1 flips up first from 011. Since there are $N!$ permutations of the order of $N$ hysterons, accounting for exchange symmetry decreases the number of candidate graphs by a factor $N!$. 
\subsubsection{Garden-of-Eden states}
\subsection{Realizability}

@@

\subsection{The base graph method}

@@

\subsubsection{Base graphs}

@@

@@

\subsubsection{Avalanches}
